---
title: "lease_knn_template"
author: "Benjamin Pope"
date: "4/27/2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#Requires odbc and caret installed 
#This creates the connection to the database and returns the query depending on if the user wants "scored" or "new" data.
get_data <- function(scored_or_new, server, user, password, database){
  library(odbc)
    con <- DBI::dbConnect(odbc::odbc(),
                        driver = "PostgreSQL Unicode(x64)",
                        database = as.character(database),
                        UID      = as.character(user),
                        PWD      = as.character(password),
                        server = as.character(server),
                        port = 5432)
  scored_lease_buildings = 'SELECT  b."CS_ID",BS."Score", b."City", b."Property_Type", b."SquareFeet",
                            b."Price_monthly", b."Expansion_sqft", b."Condition", b."Available", b."Term" 
                            FROM "Building" b 
                            RIGHT JOIN "Building_Score" BS on b."CS_ID" = BS.cs_id 
                            WHERE "Sale_Lease" = \'Lease\';'
  new_lease_buildings = 'SELECT  b."CS_ID",BS."Score", b."City", b."Property_Type", b."SquareFeet", 
                        b."Price_monthly", b."Expansion_sqft", b."Condition", b."Available", b."Term" 
                        FROM "Building" b 
                        LEFT JOIN "Building_Score" BS on b."CS_ID" = BS.cs_id
                        WHERE "Sale_Lease" = \'Lease\' AND BS."Score" IS null;'
  all_lease_buildings = 'SELECT  b."CS_ID",BS."Score", b."City", b."Property_Type", b."SquareFeet", 
                        b."Price_monthly", b."Expansion_sqft", b."Condition", b."Available", b."Term"
                        FROM "Building" b
                        LEFT JOIN "Building_Score" BS on b."CS_ID" = BS.cs_id
                        WHERE "Sale_Lease" = \'Lease\';'

  if(scored_or_new == 'scored'){
    df <- dbGetQuery(con,scored_lease_buildings)
  }
  if(scored_or_new == 'new'){
    df <- dbGetQuery(con,new_lease_buildings)
  }
  if(scored_or_new == 'all'){
    df <- dbGetQuery(con,all_lease_buildings)
  }
  return (df)
}
# This takes the data frame from get_data(), and cleans the categorical variables, normalizes numerical variables and standardizes the output data frame. 
clean_lease_data <- function(lease_df){
  library(caret)
  #  *MAY CHANGE*  We can see if expansion square feet should retain original values, or just be marked as an option.
  lease_df$Expansion_sqft <- ifelse(is.na(lease_df$Expansion_sqft),0,1)
  # TODO look into alternative way to handle missing prices (high value, mean) and see if we can eliminate them higher up the data pipeline.
  lease_df$Price_monthly <- ifelse(is.na(lease_df$Price_monthly),0,lease_df$Price_monthly)
  
  lease_df$Score <- as.factor(lease_df$Score)
  # Dummy variables with Property Type
  lease_df$Property_Type <- tolower(lease_df$Property_Type)
  pt_office_multi <- '/'
  pt_office <- list('office')
  pt_mixed <- list('flex')
  pt_other <- list('industrial','restaurant','medical','retail')
  #Start with flex to change properties that have office so that we don't double dip.
  lease_df$Property_Type <- ifelse(lease_df$Property_Type %in% pt_mixed,'PT_Flex',lease_df$Property_Type)
  lease_df$Property_Type <- ifelse(grepl(pt_office_multi, lease_df$Property_Type),'PT_Flex',lease_df$Property_Type)
  lease_df$Property_Type <- ifelse(lease_df$Property_Type %in% pt_office,'PT_Office',lease_df$Property_Type)
  lease_df$Property_Type <- ifelse(lease_df$Property_Type %in% pt_other,'PT_Other',lease_df$Property_Type)
  lease_df$Property_Type <- as.factor(lease_df$Property_Type)
  
  # Dummy variable with available
  lease_df$Available <- tolower(lease_df$Available)
  ava_now <- list('now')
  ava_30to120 <- list('30 days','60 days','90 days','120 days')
  ava_other <- list('tbd')
  ava_date <- "[0-9]$"
  lease_df$Available <- ifelse(lease_df$Available %in% ava_now,'Available_Now',lease_df$Available)
  lease_df$Available <- ifelse(lease_df$Available %in% ava_30to120,'Available_30-120_Days',lease_df$Available)
  lease_df$Available <- ifelse(lease_df$Available %in% ava_other,"Available_Other",lease_df$Available)
  lease_df$Available <- ifelse(grepl(ava_date,lease_df$Available),"Available_Other",lease_df$Available)
  lease_df$Available <- as.factor(lease_df$Available)
  
  # Dummy Variables with Term
  #  Feedback from GT for this.  what is the more important side of a term?  Something long term?  negotiable?
  #  1-10 yrs 1-5 yrs 1 yr 2-10 yrs 3-10 yrs 3-5 yrs 3 yrs 5-10 yrs 5 yrs 8-10 yrs Term_Negotiable
  lease_df$Term <- tolower(lease_df$Term)
  term_less5 <- list('1 yr','2 yrs','3 yrs','4 yrs','5 yrs','1-5 yrs','2-5 yrs','3-5 yrs','4-5 yrs')
  term_10 <- list('6 yrs', '7 yrs', '8 yrs', '9 yrs', '10 yrs','1-10 yrs','2-10 yrs','3-10 yrs','4-10 yrs','5-10 yrs','6-10 yrs','7-10 yrs','8-10 yrs','9-10 yrs')
  term_dates <- '[0-9]$'
  lease_df$Term <- ifelse(lease_df$Term %in% term_less5,'Term_short_term',lease_df$Term)
  lease_df$Term <- ifelse(lease_df$Term %in% term_10,'Term_long_term',lease_df$Term)
  lease_df$Term <- ifelse(lease_df$Term == 'negotiable','Term_Negotiable',lease_df$Term) 
  lease_df$Term <- ifelse(grepl(term_dates,lease_df$Term),'Term_Negotiable',lease_df$Term)
  lease_df$Term <- as.factor(lease_df$Term)
  
  
  # Dummy variables for city
  lease_df$City <- tolower(lease_df$City)
  city_tacoma <- list('tacoma','university place','ruston','fircrest')
  city_puy <- list('puyallup','sumner','south hill')
  city_other <- list('City_Tacoma','City_Puyallup')
  lease_df$City <- ifelse(lease_df$City %in% city_tacoma,'City_Tacoma',lease_df$City) #Groups together Tacoma
  lease_df$City <- ifelse(lease_df$City %in% city_puy,'City_Puyallup',lease_df$City) #Groups together Puyallup
  lease_df$City <- ifelse(lease_df$City %in% city_other,lease_df$City, 'City_Other') # Groups together all others into "Other"
  lease_df$City<-  as.factor(lease_df$City)
  
  dummy_city <- as.data.frame(psych::dummy.code(lease_df$City))
  dummy_property_type <- as.data.frame(psych::dummy.code(lease_df$Property_Type))
  dummy_avaliable <- as.data.frame(psych::dummy.code(lease_df$Available))
  dummy_term <- as.data.frame(psych::dummy.code(lease_df$Term))
  
  temp_lease_df <- lease_df[,c(1:2,5:7)]
  final_lease_df <- cbind(temp_lease_df,dummy_city,dummy_property_type,dummy_avaliable,dummy_term)
  
  norm.values <- caret::preProcess(final_lease_df[,3:4], method = c("center","scale"))
  final_lease_df[,3:4] <- predict(norm.values, final_lease_df[,3:4])
  
  return (final_lease_df)
}

#returns a df of the accuracy associated with each K. Requires a train.df and valid.df ran through clean_sale_data()
get_accuracy<- function(train.df,valid.df){
  #TODO either 15 or half the training rows (round if divide)
  k.num = nrow(train.df)
  if (nrow(train.df) >= 30){
    k.num <- 20
  } else {
    k.num <- ceiling(nrow(train.df)/2)
  }
  build.accuracy.df <- data.frame(k = seq(1, k.num, 1), accuracy = rep(0, k.num))
  # compute knn for different k on validation.
  for(i in 1:k.num) {
    knn.pred<- class::knn(train = train.df[,3:17], test = valid.df[,3:17], cl = train.df[,2],k=i)
    
    build.accuracy.df[i,2] <- confusionMatrix(knn.pred, valid.df$Score)$overall[1]
  }
  return(build.accuracy.df)
}

#Takes in the scored dataset and returns the optimal value for K. This requires the function get_accuracy()
find_best_knn<- function(clean_scored_data){
  trials = 100
  t.df <- data.frame(first = rep(0,trials),second = rep(0,trials), third = rep(0,trials))
  for(i in 1:trials){
    train_index <- sample(row.names(clean_scored_data),0.7*dim(clean_scored_data)[1])
    valid_index <- setdiff(row.names(clean_scored_data), train_index)
    train.df <- clean_scored_data[train_index,]
    valid.df <- clean_scored_data[valid_index,]
    
    temp.df <-get_accuracy(train.df,valid.df)
    t.df[i,1] <- order(-temp.df$accuracy)[1]
    t.df[i,2] <- order(-temp.df$accuracy)[2]
    t.df[i,3] <- order(-temp.df$accuracy)[3]
  }
  a <-table(t.df$first)*4
  b <- table(t.df$second)*2
  n <- intersect(names(a), names(b)) 
  res <- c(a[!(names(a) %in% n)], b[!(names(b) %in% n)], a[n] + b[n])
  answer <-res[order(-res)][1]
  return(as.numeric(names(answer)))
}

#Run KNN on new records and get output data frame.
for_lease_KNN_model <- function(scored_buildings, new_buildings, K){
  knn.pred.new<- class::knn(train = scored_buildings[,3:17], test = new_buildings[,3:17], cl = scored_buildings[,2],k=K)
  outscore <- as.data.frame(knn.pred.new)
  cs_id <- new_buildings$CS_ID
  model_number <- 13 #utils::capture.output(cat("for_sale_KNN_",K,sep =""))
  date <- Sys.Date()
  output <- cbind(cs_id,model_number,outscore,date)
  setnames(output, (c( "CS_ID", "model_id", "score", "date_calculated")))
  return (output)
}
main_forlease_knn <- function(user, password, server, database){ 
  #Get data frame of scored buildings 
  building.scores <- get_data('scored',as.character(server),as.character(user),as.character(password),as.character(database))
  #Get data frame of new buildings
  new.buildings <- get_data('all',as.character(server),as.character(user),as.character(password),as.character(database))
  #Clean scored buildings
  clean_scored_data <- clean_lease_data(building.scores)
  #Clean new buildings
  clean_new_data <- clean_lease_data(new.buildings)
  #Optimize best K, run model on new data, return output of scores and model information
  knn.scores <- for_lease_KNN_model(clean_scored_data, clean_new_data,find_best_knn(clean_scored_data))
  return(knn.scores)
}
```


```{r}
lease_scored <- get_data('scored',"greentrike.cfvgdrxonjze.us-west-2.rds.amazonaws.com","bpope","somepassword","TEST")

lease_new <- get_data('new',"greentrike.cfvgdrxonjze.us-west-2.rds.amazonaws.com","bpope","somepassword","TEST")

lease_all <- get_data('all',"greentrike.cfvgdrxonjze.us-west-2.rds.amazonaws.com","bpope","somepassword","TEST")


clean_new_buildings <- clean_lease_data(lease_new)
clean_all_buildings <- clean_lease_data(lease_all)

```
Things to consider:
  1.NA values
    expansion sqft
    price
  2.ensure integer are double precision
    done in SQL import, or r?
  3.dummy variables
    which ones are necessary for MVP?
      choose from (city, property_type, avaliable, term)
    How to handle edge cases / new categories for each variable
      function to analyze and sort variables
      cutoff point for variables (example, city has 3 variables: Tacoma, Puyallup, other)
  4.ensure columns will remain in order
    must lock dummy variable length *OR* ensure columns match for train to validate.
