---
title: "lease_knn_template"
author: "Benjamin Pope"
date: "4/27/2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#Requires odbc and caret installed 
```

```{r}
get_data <- function(scored_or_new, server, user, password, database,model_number){
  library(odbc)
  scored_lease_buildings = 'SELECT  b."CS_ID",BS."Score", b."City", b."Property_Type", b."SquareFeet", b."Price_monthly", b."Expansion_sqft", b."Condition", b."Available", b."Term" FROM "Building" b RIGHT JOIN "Building_Score" BS on b."CS_ID" = BS.cs_id WHERE "Sale_Lease" = \'Lease\';'

new_lease_buildings = 'SELECT  b."CS_ID",BS."Score", b."City", b."Property_Type", b."SquareFeet", b."Price_monthly", b."Expansion_sqft", b."Condition", b."Available", b."Term" FROM "Building" b LEFT JOIN "Building_Score" BS on b."CS_ID" = BS.cs_id WHERE "Sale_Lease" = \'Lease\' AND BS."Score" IS null;'

  con <- DBI::dbConnect(odbc::odbc(),
  driver = "PostgreSQL Unicode(x64)",
  database = as.character(database),
  UID      = as.character(user),
  PWD      = as.character(password),
  server = as.character(server),
  port = 5432)
  if(scored_or_new == 'scored'){
    df <- dbGetQuery(con,scored_lease_buildings)
  }
  if(scored_or_new == 'new'){
    df <- dbGetQuery(con,new_lease_buildings)
  }
  return (df)
}
```

```{r}
lease_scored <- get_data('scored',"greentrike.cfvgdrxonjze.us-west-2.rds.amazonaws.com","bpope","somepassword","TEST")

lease_new <- get_data('new',"greentrike.cfvgdrxonjze.us-west-2.rds.amazonaws.com","bpope","somepassword","TEST")
```

Things to consider:
  1.NA values
    expansion sqft
    price
  2.ensure integer are double precision
    done in SQL import, or r?
  3.dummy variables
    which ones are necessary for MVP?
      choose from (city, property_type, avaliable, term)
    How to handle edge cases / new categories for each variable
      function to analyze and sort variables
      cutoff point for variables (example, city has 3 variables: Tacoma, Puyallup, other)
  4.ensure columns will remain in order
    must lock dummy variable length *OR* ensure columns match for train to validate.
    
```{r}
clean_lease_data <- function(dataframe){
  lease_df = dataframe
  library(caret)
  #  *MAY CHANGE*  We can see if expansion square feet should retain original values, or just be marked as an option.
  lease_df$Expansion_sqft <- ifelse(is.na(lease_df$Expansion_sqft),0,1)
  # TODO look into alternative way to handle missing prices (high value, mean) and see if we can eliminate them higher up the data pipeline.
  lease_df$Price_monthly <- ifelse(is.na(lease_df$Price_monthly),0,lease_df$Price_monthly)
  
  lease_df$Score <- as.factor(lease_df$Score)
  # Dummy variables with Property Type
  pt_office <- '(Office|office)'
  pt_mixed <- '(/|Flex)'
  pt_other <- '(Industrial|Restaurant|Medical|Retail)'
  #Start with flex to change properties that have office so that we don't double dip.
  lease_df$Property_Type <- ifelse(grepl(pt_mixed,lease_df$Property_Type),'PT_Flex',lease_df$Property_Type)
  lease_df$Property_Type <- ifelse(grepl(pt_office,lease_df$Property_Type),'PT_Office',lease_df$Property_Type)
  lease_df$Property_Type <- ifelse(grepl(pt_other,lease_df$Property_Type),'PT_Other',lease_df$Property_Type)
  lease_df$Property_Type <- as.factor(lease_df$Property_Type)
  
  # Dummy variable with available
  ava_now <- "(Now|now)"
  ava_30to120 <- "(30 Days|60 Days|90 Days|120 Days)"
  ava_other <- "TBD"
  ava_date <- "[0-9]$"
  lease_df$Available <- ifelse(grepl(ava_now,lease_df$Available),'Available_Now',lease_df$Available)
  lease_df$Available <- ifelse(grepl(ava_30to120,lease_df$Available),'Available_30-120_Days',lease_df$Available)
  lease_df$Available <- ifelse(grepl(ava_date,lease_df$Available),"Available_Other",lease_df$Available)
  lease_df$Available <- ifelse(grepl(ava_other,lease_df$Available),"Available_Other",lease_df$Available)
  lease_df$Available <- as.factor(lease_df$Available)
  
  # Dummy Variables with Term
  #  Feedback from GT for this.  what is the more important side of a term?  Something long term?  negotiable?
  term_less5 <- '^[0-5] Yrs|1 Yr|^[0-5]-[2-5] Yrs'
  term_10less <- '[0-9]-[1]'
  term_dates <- '[0-9]$'
   
  lease_df$Term <- ifelse(grepl(term_less5,lease_df$Term),'Term_short_term',lease_df$Term)
  lease_df$Term <- ifelse(grepl(term_10less,lease_df$Term),'Term_long_term',lease_df$Term)
  lease_df$Term <- ifelse(grepl(term_dates,lease_df$Term),'Term_Negotiable',lease_df$Term)
  lease_df$Term <- ifelse(lease_df$Term == 'Negotiable','Term_Negotiable',lease_df$Term)
  lease_df$Term <- as.factor(lease_df$Term)
  
  # Dummy variables for city
  city_tacoma <- "(Tacoma|University Place|Ruston|Fircrest)"
  city_puy <- '(Puyallup|Sumner|South hill)'
  city_other <- '(City_Tacoma|City_Puyallup)'
  lease_df$City <- ifelse(grepl(city_tacoma,lease_df$City),'City_Tacoma',lease_df$City) #Groups together Tacoma
  lease_df$City <- ifelse(grepl(city_puy,lease_df$City),'City_Puyallup',lease_df$City) #Groups together Puyallup
  lease_df$City <- ifelse(grepl(city_other,lease_df$City),lease_df$City, 'City_Other') # Groups together all others into "Other"
  lease_df$City<-  as.factor(lease_df$City)
  
  dummy_city <- as.data.frame(psych::dummy.code(lease_df$City))
  dummy_property_type <- as.data.frame(psych::dummy.code(lease_df$Property_Type))
  dummy_avaliable <- as.data.frame(psych::dummy.code(lease_df$Available))
  dummy_term <- as.data.frame(psych::dummy.code(lease_df$Term))
  
  temp_lease_df <- lease_df[,c(1:2,5:7)]
  final_lease_df <- cbind(temp_lease_df,dummy_city,dummy_property_type,dummy_avaliable,dummy_term)
  
  norm.values <- caret::preProcess(final_lease_df[,3:4], method = c("center","scale"))
  final_lease_df[,3:4] <- predict(norm.values, final_lease_df[,3:4])
  
  return (final_lease_df)
}
```

```{r}
cleaned_lease_scored <- clean_lease_data(lease_scored)
cleaned_lease_new <- clean_lease_data(lease_new)
```

```{r}
#Function to normalize and create dummy variables
train_index <- sample(row.names(cleaned_lease_scored),round(0.7*dim(cleaned_lease_scored)[1]))
valid_index <- setdiff(row.names(cleaned_lease_scored),train_index)
train.df <- cleaned_lease_scored[train_index,]
valid.df <- cleaned_lease_scored[valid_index,]
```

```{r}
#run KNN tests to find best k
find_best_knn <- function(train_dataframe,valid_dataframe){
  k.num = nrow(train.df)
  build.accuracy.df <- data.frame(k = seq(1, k.num, 1), accuracy = rep(0, k.num))
# compute knn for different k on validation.
  for(i in 1:k.num) {
    knn.pred<- class::knn(train = train.df[,3:17], test = valid.df[,3:17], cl = train.df[,2],k=i)
  
    build.accuracy.df[i,2] <- confusionMatrix(knn.pred, valid.df$Score)$overall[1]
  }
  return(build.accuracy.df)
}
```

```{r}
#
for_lease_KNN <- function(clean_scored_buildings, clean_new_buildings, K){
  knn.pred.new<- class::knn(train = clean_scored_buildings[,3:17], test = clean_new_buildings[,3:17], cl = clean_scored_buildings[,2],k=K)
  return(knn.pred.new)
}
```

```{r}
#Create Dataframe for dynamic export
create_output <- function(predicted_values, model_name){
  outscore <- as.data.frame(predicted_values)
  cs_id <- clean_new_data$CS_ID
  model_number <- model_name
  date <- Sys.Date()
  output <- cbind(cs_id, model_number, outscore, date)
  setnames(output, (c( "cs_id", "model_id", "score", "date_calculated")))
  return (output)
}
```

